### 2019-06-04 thesis.tex
Added one more paragraph to the section
* thesis.tex: Summary: Added section about collective processes

Collective behavior is a necessary condition for an ionized to be
considered a plasma. As a fundamental characteristic, it occurs in
plasmas that exhibit overall neutrality, the so-called neutral
plasmas, and also in nonneutral plasmas.

>>>>

Collective processes are the outcome of collective behavior, i.e.,
are processes that occur as a response of the collective behavior
of the plasma. Such phenomena exists in both neutral (same number of
negative and positive components), and nonneutral (different quantities
of negative and positive charges, or have only one charge species)
plasmas. The dynamics in both cases, however, is dramatically different.
In this work we are interested only in the first case and, once we
